Template for GTEx example on cluster

### 2017-10-06 analysis/GTEXzscoreTemplate.Rmd
Files commited by wflow_commit.

### plot SFA result

@@

>>>>

### plot SFA result K = 30

@@

### plot of SFA result with t(Y) K = 10

```{r}
gt10 = readRDS('../data/GTExdata/SFAres/sfaTYK_10.rds')

par(mfrow = c(2,3),mar=c(5.1,4.1,4.1,2.1)-1.9)
for(k in 1:10){
  barplot(gt10$L[,k],main = paste("factor",k))
}
```

#### problem in K = 20 and K = 30 in this case.

```
gsl: lu.c:147: ERROR: matrix is singular
Default GSL error handler invoked.
```
